Deployable Probabilistic Programming

### 2019-08-11 paper/paper.tex

  Our attitude differs from the established approach in that
  instead of proposing yet another probabilistic programming
  language, either genuinely different~\cite{MMR+07,Stan17} or
  derived from an existing general-purpose programming
  language by extending the syntax or changing the
  semantics~\cite{GMR+08,TMY+16,GXG18}, we advocate enabling
  probabilistic inference on models written in a
  general-purpose probabilistic programming language, the same
  one as the language used to program the bulk of the system.
  We formulate guidelines for such implementation, and, based
  on the guidelines, introduce a probabilistic programming
  facility for the Go programming language~\cite{Golang}. By
  explaining our implementation choices and techniques,
  we argue that a similar facility can be added to any modern
  general-purpose programming language, giving a
  production system modeling and inference capabilities which
  do not fall short from and sometimes exceed those of
  probabilistic programming-centric frameworks with custom
  languages and runtimes. Availability of such facilities
  in major general-purpose programming languages would free
  probabilistic programming researchers and practitioners
  alike from language wars~\cite{SH14} and foster practical
  applications of probabilistic programming.

>>>>

  Our attitude differs from the established approach in that
  instead of proposing yet another probabilistic programming
  language, either genuinely different~\cite{MMR+07,Stan17} or
  derived from an existing general-purpose programming
  language by extending the syntax or changing the
  semantics~\cite{GMR+08,TMY+16,GXG18}, we advocate enabling
  probabilistic inference on models written in a
  general-purpose probabilistic programming language, the same
  one as the language used to program the bulk of the system.
  We formulate guidelines for such implementation, and, based
  on the guidelines, introduce a probabilistic programming
  facility for the Go programming language~\cite{Golang}. By
  explaining our implementation choices and techniques,
  we argue that a similar facility can be added to any modern
  general-purpose purpose programming language, giving a
  production system modeling and inference capabilities which
  do not fall short from and sometimes exceed those of
  probabilistic programming-centric frameworks with custom
  languages and runtimes. Availability of such facilities
  in major general-purpose programming languages would free
  probabilistic programming researchers and practitioners
  alike from language wars~\cite{SH14} and foster practical
  applications of probabilistic programming.
